---
title: "R Notebook"
output: html_notebook
---

# LOAD DATASETS PACKAGES 

```{r}
library(datasets)  # Load/unload base packages manually
```

# LOAD DATA

```{r}
head(iris) 
```


#Basic plots

plot() -> Basix x-y plotting

```{r}

plot(iris$Species) #Categorical variable

```

```{r}
 
plot(iris$Sepal.Length) # Quantitative variable

```


```{r}

plot(iris$Species, iris$Petal.Width)  # Categorical x Quantitative

```

```{r}
plot(iris$Petal.Length, iris$Petal.Width)  # Quant pair
```

```{r}
plot(iris)  # Entire data frame
```


```{r}
# Plot with options
plot(iris$Petal.Length, iris$Petal.Width,
  col = "#FB8DA0",  # Hex code for datalab.cc pink
  pch = 8,       # Use star for points
  main = "Iris: Petal Length vs. Petal Width",
  xlab = "Petal Length",
  ylab = "Petal Width")

```

# PLOT FORMULAS WITH PLOT()

```{r}

plot(cos, 0, 2*pi)

```

```{r}
plot(cos, -pi, 2*pi) 
```
```{r}
plot(exp, 1, 5)
```
## dnorm function
This function returns the value of the probability density function (pdf) of the normal distribution given a certain random variable x, a population mean μ, and the population standard deviation σ. 

Syntax; dnorm(x, mean, sd)

x: vector of quantiles.
mean: vector of means.
sd: vector standard deviation


```{r}

plot(dnorm, -3, +3)

```

```{r}

# Formula plot with options
plot(dnorm, -3, +3,
  col = "#FB8DA0",
  lwd = 5,
  main = "Standard Normal Distribution",
  xlab = "z-scores",
  ylab = "Density")

```
# CLEAN UP

```{r}

# Clear packages
detach("package:datasets", unload = TRUE)

```


```{r}
# Clear console
cat("\014")  # ctrl+L
```

